Seasonal Variations in Marriage License Applications

### 2024-09-27 paper/paper.qmd
fig 4 width change

```{r}
#| label: fig-december-plot
#| fig-cap: "Total Marriage Licenses Issued in December (2011-2023)"
#| echo: false
#| warning: false
#| message: false
#| 
# Filter for December and calculate the total number of licenses (this acts like a December summary table)
december_data <- data %>%
  filter(month == "12") %>%  # Filter for December
  group_by(year) %>%  # Group by year
  summarise(december_licenses = sum(marriage_licenses))  # Summarize total licenses in December

@@

```
# Discussion {#sec-disc}

>>>>

```{r}
#| label: fig-december-plot
#| fig-cap: "Total Marriage Licenses Issued in December (2011-2023)"
#| echo: false
#| warning: false
#| message: false
#| fig-width: 4
#| fig-height: 2
# Filter for December and calculate the total number of licenses (this acts like a December summary table)
december_data <- data %>%
  filter(month == "12") %>%  # Filter for December
  group_by(year) %>%  # Group by year
  summarise(december_licenses = sum(marriage_licenses))  # Summarize total licenses in December

@@

```
\newpage 
# Discussion {#sec-disc}
